---
title: "Developing Data Products"
subtitle: "Course Project Week 4: Shiny App & Reproducible Pitch"
author: "David Arcos"
date: "2023-07-25"
output:
  ioslides_presentation: default
  html_document:
    number_sections: yes
mode: selfcontained
job: Reproducible Pitch Presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(gapminder)
```

## Project Overview

Using an excert of the Gapminder data, this Shiny App shows: 

- The relationship between the life expectancy and GDP per capita, by continent.
- The relationship between the life expectancy and GDP per capita, by country.
- The whole data for a single country, presented in a table format.

The deployed application in the Shiny server can be found in the flollowing link:

- [Shiny App](https://pages.github.com/)

The source code repository link is: 

- [GitHub Repository](https://pages.github.com/)

## Data for analysis

This Shiny App uses the *Gapminder* dataset, which consists of an excerpt of the Gapminder data on life expectancy, GDP per capita and population by country between 1952 and 2007. 

```{r, include=TRUE, echo=TRUE, warning=FALSE,message=FALSE}
data("gapminder")
head(gapminder)
```

## Application Panel

### Sidebar Panel:

- A `selectInput` widget to select continents or a single country
- A `sliderInput` widget to select the range of years to present the data
- A `checkboxInput` widget to show the data for each country selected.

### Main Panel 

- Two `scatterplots` about the relationship between life expectancy and GDP per capita
- If the checkbox is marked, a `data table` will be shown with the whole data for a single country.


## User Manual

Once the app is open: 

1. Select one or more continents to show in **Plot 1** how are life expectancy and GDP per capita related.
2. Select one country at a time to show in **Plot 2** how are life expectancy and GDP per capita related in a single country.
3. Also, you can check the box to show a **Data table** with all the data from 1952 to 2007 for the selected country in the previous step.




